Reply to reviewers\\ LMCS \#\,6784 Manuscript: \\``Compositional equivalences based on Open pNets''

### 2021-10-22 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
typos and lmcs style
small typos

\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more generaly for a process algebra with a choice operator and a $\tau$ action)

\item We improved explanations wherever the reviewers indicated it was necessary (e.g.  semantics of pNets,  definition of bisimulation, definition of weak open transitions)

@@

- I was left unconvinced that using open automata as an intermediary structure to define the bisimualtion relations is the best approach to develop this material.  The authors should give more convincing argument that such definitions could not be adequately defined directly on pNets (an already complex framework).  It left me wondering:
1) How do you validate the translation of pNets to Open Automata?  Shouldn't there be some result that states that the translation is semantic preserving?   
\begin{quote}
Indeed such a theorem could be stated and proven: the two semantics are behaviourally equivalent, this would be proven by exhibiting a complex bisimulation between the two models, restricted only on the closed non-parametric part. In practice a proof of equivalence would make the article much longer with a lot of technical developments; we believe it would make the article more difficult to read. However we added a discussion on equivalence between semantics at the end of Section 2.2.
\end{quote}

@@

" Bisimulation over a symbolic and open model like open pNets or open automata is  different from the classical notion of bisimulation because it cannot rely on the equality over a finite set of action labels. Classical bisimulations require to exhibit, for each transition of one system, a transition of the other system that simulates it. Instead, bisimulation for open automata  rely on the simulation of each open transition of one automaton by a set of open transitions of the other one, that should cover all the 
cases where the original transition can be triggered.
"

@@

- In general, weak bisimulation is *not* a congruence for all types of interacting contexts.  For instance, in the case of CCS, the classsical counter example is that whereas 
tau.a.0  \\bisim  a.0
we do *not* have
tau.a.0 + b.0 \\bisim  a.0 + b.0 
Given the generality of the pNets framework I found the claim stated in Theorem 7 to be suspicious (and hard to ascertain).  The authors should perhaps provide more intuition why this is the case for their framework.

>>>>

\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more generally for a process algebra with a choice operator and a $\tau$ action).

\item We improved explanations wherever the reviewers indicated it was necessary (e.g.  semantics of pNets,  definition of bisimulation, definition of weak open transitions).

@@

- I was left unconvinced that using open automata as an intermediary structure to define the bisimulation relations is the best approach to develop this material.  The authors should give more convincing argument that such definitions could not be adequately defined directly on pNets (an already complex framework).  It left me wondering:
1) How do you validate the translation of pNets to Open Automata?  Shouldn't there be some result that states that the translation is semantic preserving?   
\begin{quote}
Indeed such a theorem could be stated and proven: the two semantics are behaviourally equivalent, this would be proven by exhibiting a complex bisimulation between the two models, restricted only on the closed non-parametric part. In practice a proof of equivalence would make the article much longer with a lot of technical developments; we believe it would make the article more difficult to read. However we added a discussion on equivalence between semantics at the end of Section 2.2.
\end{quote}

@@

" Bisimulation over a symbolic and open model like open pNets or open automata is  different from the classical notion of bisimulation because it cannot rely on the equality over a finite set of action labels. Classical bisimulations require to exhibit, for each transition of one system, a transition of the other system that simulates it. Instead, bisimulation for open automata  relies on the simulation of each open transition of one automaton by a set of open transitions of the other one, that should cover all the 
cases where the original transition can be triggered.
"

@@

- In general, weak bisimulation is *not* a congruence for all types of interacting contexts.  For instance, in the case of CCS, the classical counter example is that whereas 
tau.a.0  \\bisim  a.0
we do *not* have
tau.a.0 + b.0 \\bisim  a.0 + b.0 
Given the generality of the pNets framework I found the claim stated in Theorem 7 to be suspicious (and hard to ascertain).  The authors should perhaps provide more intuition why this is the case for their framework.
